---
title: "cv"
---

## Data driven CV

No lock-in

Inspired heavily the the usethis package, datadrivencv strives to make itself unnecessary.
The main function is use_data_driven_cv, which sets up the files you need to build your CV.
These files are self-contained meaning if you uninstall datadrivencv your CV will still knit fine.
All the R code logic is contained in a sourced script so if you want to change it you can do so.

The package aims to bootstrap you to a working data-driven CV pipeline.
Serving as a jumping off point for you to build your own custom CV, you may at first want to leave it as is and then slowly tweak things to keep it fresh.
You have all the code, so you can!
Using it

The first step to using the package is the use_data_driven_cv() function.
This function takes a few input parameters and when when run, sets up a series of files in your current working directory.
E.g.

```{r}
# run ?datadrivencv::use_datadriven_cv to see more details
datadrivencv::use_datadriven_cv(
  full_name = "Nick Strayer",
  data_location = "https://docs.google.com/spreadsheets/d/14MQICF2F8-vf8CKPF1m4lyGKO6_thG-4aSwat1e2TWc",
  pdf_location = "https://github.com/nstrayer/cv/raw/master/strayer_cv.pdf",
  html_location = "nickstrayer.me/cv/",
  source_location = "https://github.com/nstrayer/cv"
)
```

```{r}
# Make a temp directory for placing files
# This would be a real location for a typical situation
temp_dir <- fs::dir_create(fs::path(tempdir(), "my_cv"))

datadrivencv::use_datadriven_cv(
  full_name = "Joey Trampush",
  pdf_location = "https://github.com/brainworkup/cv/blob/main/trampush_cv.pdf",
  source_location = "https://github.com/brainworkup/cv"
)



use_datadriven_cv(
  full_name = "Nick Strayer",
  data_location = "https://docs.google.com/spreadsheets/d/14MQICF2F8-vf8CKPF1m4lyGKO6_thG-4aSwat1e2TWc",
  pdf_location = "https://github.com/nstrayer/cv/raw/master/strayer_cv.pdf",
  html_location = "nickstrayer.me/cv/",
  source_location = "https://github.com/nstrayer/cv",
  output_dir = temp_dir,
  open_files = FALSE
)

# Files should be where they were requested
list.files(temp_dir)#> [1] "cv_printing_functions.r" "cv.rmd"                 
#> [3] "dd_cv.css"               "render_cv.r"            

```

```{r}
datadrivencv::use_csv_data_storage(folder_name = "data", create_output_dir = TRUE)
```
## vitae: Dynamic CVs with R Markdown

vitae for R

The vitae package is now available on CRAN, making it easy to install with:

```{r}
install.packages("vitae")
```

In version 0.1.0, the vitae package provides four commonly used LaTeX CV templates that have been modified for use with R Markdown.
With the vitae package installed, CV templates can be accessed from the RStudio R Markdown template selector:

```{r}
library(datadrivencv)
library(vitae)
```


```{r}
# Knit the HTML version
rmarkdown::render("cv.rmd",
                  params = list(pdf_mode = FALSE),
                  output_file = "cv.html")

# Knit the PDF version to temporary html location
tmp_html_cv_loc <- fs::file_temp(ext = ".html")
rmarkdown::render("cv.rmd",
                  params = list(pdf_mode = TRUE),
                  output_file = tmp_html_cv_loc)

# Convert to PDF using Pagedown
pagedown::chrome_print(input = tmp_html_cv_loc,
                       output = "trampush_cv.pdf")
```
